---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# affiliationExplorer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of affiliationExplorer is to provide a user-friendly graphical interface to choose between different conflicting affiliations. 

You need to provide to upload two files to the application:

- a `biom` file
- a multihits file (typically called `multihits_blabla.tsv`)

The app will then sort the multi-affiliated taxa from most abundant to least abundant and help you pick one (or none) of the conflicting affiliations. You can also edit the affiliation manually. 

Finally, use the `Download` button to download the biom file with corrected affiliations. This cleaned biom can be parsed with `import_frogs()` from the `phyloseq.extended` [package](https://github.com/mahendra-mariadassou/phyloseq-extended/tree/dev)

**Note** `affiliationExplorer` uses short taxa names, which may differ from the original names, in the display. However, names from the original biom file are preserved in the cleaned biom. 

## Installation

You can install the latest version of `affiliationExplorer` from [github](https://github.com/mahendra-mariadassou/affiliationExplorer) with:

``` r
## install.packages("remotes")
remotes::install_github("mahendra-mariadassou/affiliationExplorer")
```

## Launching the app

You can launch on your computer as follows:

```{r example, eval = FALSE}
library(affiliationExplorer)
affiliationExplorer::run_app()
```

